On the combination of Set Functions and Failures

### 2012-05-30 docs/src/manual.tex
Some improvement for "make"

\begin{titlepage}
\pdfbookmark[1]{Title}{Title}
\begin{center}
\fbox{
\begin{minipage}[t]{\figurewidth}
\begin{center}\vspace{10ex}
{\Huge\bf KiCS2 0.2}\\[4ex]
{\huge The Kiel Curry System (Version 2)}\\[7ex]
{\huge User Manual}\\[4ex]
Version of May 16, 2012\\[6ex]
\Large
Michael Hanus$^1$ [editor] \\[3ex]
{\large Additional Contributors:}\\[2ex]
Bernd Bra\ss{}el$^2$ \\
Bj\"orn Peem\"oller$^3$\\
Fabian Reck$^4$ \\[4ex]
\normalsize
(1) University of Kiel, Germany, {\tt mh@informatik.uni-kiel.de} \\
(2) University of Kiel, Germany, {\tt bbr@informatik.uni-kiel.de} \\
(3) University of Kiel, Germany, {\tt bjp@informatik.uni-kiel.de} \\
(4) University of Kiel, Germany, {\tt fre@informatik.uni-kiel.de} \\[5ex]~
\end{center}
\end{minipage}}
\end{center}
\end{titlepage}

@@

Installation instructions for KiCS2 can be found in
the file \code{INSTALL.txt} stored in the KiCS2 installation directory.
Note that there are two possibilities to install KiCS2:
\begin{description}
\item[Global installation:]\index{global installation}\index{installation!global}
KiCS2 is installed in some global system directory where users
have no write permission. In this case, some options for experimenting
with KiCS2 (like \code{supply} or \code{ghc}, see below)
are not available (since they require the recompilation of parts of
the installed system).
\item[Local installation:]\index{local installation}\index{installation!local}
KiCS2 is installed in some local user directory where the user
has write permission. The requires the setting of the option
\begin{lstlisting}
GLOBALINSTALL=no
\end{lstlisting}
in the \code{Makefile} of the KiCS2 installation.
In this case, all options of KiCS2 are available.
\end{description}
In the following, $kics2home$ denotes the installation directory
of the KiCS2 installation.

>>>>

\begin{titlepage}
\pdfbookmark[1]{Title}{Title}
\begin{center}
\fbox{
\begin{minipage}[t]{\figurewidth}
\begin{center}\vspace{10ex}
{\Huge\bf KiCS2 0.2}\\[4ex]
{\huge The Kiel Curry System (Version 2)}\\[7ex]
{\huge User Manual}\\[4ex]
Version of May 30, 2012\\[6ex]
\Large
Michael Hanus$^1$ [editor] \\[3ex]
{\large Additional Contributors:}\\[2ex]
Bernd Bra\ss{}el$^2$ \\
Bj\"orn Peem\"oller$^3$\\
Fabian Reck$^4$ \\[4ex]
\normalsize
(1) University of Kiel, Germany, {\tt mh@informatik.uni-kiel.de} \\
(2) University of Kiel, Germany, {\tt bbr@informatik.uni-kiel.de} \\
(3) University of Kiel, Germany, {\tt bjp@informatik.uni-kiel.de} \\
(4) University of Kiel, Germany, {\tt fre@informatik.uni-kiel.de} \\[5ex]~
\end{center}
\end{minipage}}
\end{center}
\end{titlepage}

@@

Installation instructions for KiCS2 can be found in
the file \code{INSTALL.txt} stored in the KiCS2 installation directory.
Note that there are two possibilities to install KiCS2:
\begin{description}
\item[Global installation:]\index{global installation}\index{installation!global}
KiCS2 is installed in some global system directory where users
have no write permission. In this case, some options for experimenting
with KiCS2 (like \code{supply} or \code{ghc}, see below)
are not available (since they require the recompilation of parts of
the installed system).
\item[Local installation:]\index{local installation}\index{installation!local}
KiCS2 is installed in some local user directory where the user
has write permission and the option \code{GLOBALINSTALL}
in the \code{Makefile} of the KiCS2 installation is set as follows:
\begin{lstlisting}
GLOBALINSTALL=no
\end{lstlisting}
In this case, all options of KiCS2 are available.
\end{description}
In the following, $kics2home$ denotes the installation directory
of the KiCS2 installation.
